Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-16 paper/main.tex
Some modifications to chosen sha3-implementations

The chosen implementations are shown in Table \ref{tbl:sha3:implementations}
and their compiler flags used, which are extracted from the \ac{SUPERCOP}
results can be seen in Table\ref{tbl:sha3:compilerflags}. It should be noted
that 32 in blake32 does not refer to the output length of the function, but the
fact that the algorithm is optimized for 32-bit usage. 512 in Keccackc512 also
does not mean 512-bit output, but 512 cycles in the internal function. The
relative speeds of the implementations chosen compared to the best version in
\ac{SUPERCOP} and relative speed of the benchmark compared to other candidates
can bee seen in Table \ref{tbl:sha3:speedrelative}. For the most part we have
found working versions of all candidates in \ac{SUPERCOP}, however there are
some exceptions.

@@

>>>>

The chosen implementations are shown in Table \ref{tbl:sha3:implementations}
and their compiler flags used, which are extracted from the \ac{SUPERCOP}
results can be seen in Table\ref{tbl:sha3:compilerflags}. It should be noted
that 32 in blake32 does not refer to the output length of the function, but the
fact that the algorithm is optimized for 32-bit usage. 512 in Keccackc512 also
does not mean 512-bit output, but 512 cycles in the internal function. The
relative speeds of the implementations chosen compared to the best version in
\ac{SUPERCOP} and relative speed of the benchmark compared to other candidates
can bee seen in Table \ref{tbl:sha3:speedrelative}. It should also be noted
that the fastest sha256 implementation in \ac{SUPERCOP} is
cryptopp\footnote{\url{http://www.cryptopp.com/}}, which is the one used by
Tahoe-\ac{LAFS}. For the most part we have found working versions of all
candidates in \ac{SUPERCOP}, however there are some exceptions.

@@

\paragraph{Shavite3} seems to have received an update\footnote{see
\url{http://www.cs.technion.ac.il/~orrd/SHAvite-3/}}. We have observed that
implementations of Shavite3 in \ac{SUPERCOP}-20101014 or later seems to fail to
verify the \ac{KAT}s, while the version we have used does. We believe this is
only because newer \ac{KAT}s will have to be generated, but since the author
has not done so we chose to use an older version of the algorithm.

### 2010-11-16 paper/tables/sha3_flags.tex
Added more to the candidate selection section
Some modifications to chosen sha3-implementations

\begin{table}
  \centering
  \begin{tabular}{ | l | l | }
    \hline
    \textbf{candidate} & \textbf{from}  \\ \hline
     blake       & mssse3 -m32 -march=native -mtune=native -O -fomit-frame-pointer  \\ \hline
     bmw         & -funroll-loops -m32 -march=pentium4 -O3 -fomit-frame-pointer     \\ \hline
     cubehash    & none                                                             \\ \hline
     echo        & -funroll-loops -m32 -march?prescott -O2 -fomit-frame-pointer     \\ \hline
     fugue       & -funroll-loops -O -fomit-frame-pointer                           \\ \hline
     groestl     & -m32 -march=pentium3 -O -fomit-frame-pointer                     \\ \hline
     hamsi       & -msse2 -funroll-loops -m32 -march=pentium-m -O3 -fomit-frame-pointer\\ \hline
     jh          & none                                                             \\ \hline
     keccak      & -msse2 -march=barcelona -O3 -fomit-frame-pointer                 \\ \hline
     luffa       & -msse2 -funroll-loops -march=k8 -O3 -fomit-frame-pointer         \\ \hline
     shabal      & -funroll-loops -m32 -march=pentium2 -O -fomit-frame-pointer      \\ \hline
     shavite3    & -funroll-loops -march=i486 -O -fomit-frame-pointer               \\ \hline
     simd        & -m32 -march=barcelona -O2 -fomit-frame-pointer                   \\ \hline
     skein       & -march=pentium2 -O2 -fomit-frame-pointer                         \\ \hline
  \end{tabular}
  \caption{\ac{GCC} compiler flags used for the implementations}
  \label{tbl:sha:compilerflags}
\end{table}

>>>>

\begin{table}
  \centering
  \begin{tabular}{ | l | l | }
    \hline
    \textbf{candidate} & \textbf{from}  \\ \hline
     blake       & mssse3 -m32 -march=native -mtune=native -O -fomit-frame-pointer  \\ \hline
     bmw         & -funroll-loops -m32 -march=pentium4 -O3 -fomit-frame-pointer     \\ \hline
     cubehash    & none                                                             \\ \hline
     echo        & -funroll-loops -m32 -march?prescott -O2 -fomit-frame-pointer     \\ \hline
     fugue       & -funroll-loops -O -fomit-frame-pointer                           \\ \hline
     groestl     & -m32 -march=pentium3 -O -fomit-frame-pointer                     \\ \hline
     hamsi       & -msse2 -funroll-loops -m32 -march=pentium-m -O3 -fomit-frame-pointer\\ \hline
     jh          & -m32 -march=core2 -msse4.1 -O -fomit-frame-pointer               \\ \hline
     keccak      & -msse2 -march=barcelona -O3 -fomit-frame-pointer                 \\ \hline
     luffa       & -msse2 -funroll-loops -march=k8 -O3 -fomit-frame-pointer         \\ \hline
     shabal      & -funroll-loops -m32 -march=pentium2 -O -fomit-frame-pointer      \\ \hline
     shavite3    & -funroll-loops -march=i486 -O -fomit-frame-pointer               \\ \hline
     simd        & -m32 -march=barcelona -O2 -fomit-frame-pointer                   \\ \hline
     skein       & -march=pentium2 -O2 -fomit-frame-pointer                         \\ \hline
  \end{tabular}
  \caption{\ac{GCC} compiler flags used on the implementations}
  \label{tbl:sha3:compilerflags}
\end{table}
